% Significantly edited from its original form by Joseph Woodruff
%
% Template (C) 2004-2010 - Jason R. Blevins
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{helvet}
\usepackage{changepage,titlesec}
\usepackage{fancyhdr}

\titlespacing*{\section}{0pt}{0.75\baselineskip}{0.5\baselineskip}
\titlespacing*{\subsection}{0pt}{0.5\baselineskip}{0.25\baselineskip}

\renewcommand{\familydefault}{\sfdefault}

\newcommand{\name}{Joseph Woodruff}

\title{\name's Resume}

\newcommand{\address}{21507 42nd Ave S Apt C2}
\newcommand{\city}{Seatac}
\newcommand{\state}{WA}
\newcommand{\zip}{98198}

\newcommand{\phone}{(503) 704-1329}

\newcommand{\email}{\href{mailto:joseph.woodruff@a7m2.me}{joseph.woodruff@a7m2.me}}

\newcommand{\webpage}{www.linkedin.com/in/jawoodru}

\newcommand{\skills}{C, C++, Git, make, CMake, Matlab, Simulink, Linux, Python, DOORS, JIRA, Embedded Development, ThreadX, DO-178B/C, Board bring-up, Oscilloscope serial protocol troubleshooting}


% Fedora, Redhat Enterprise Linux (RHEL), Ubuntu, Debian, SUSE, Intel Platform Open Cluster Stack, ROCKS Cluster, \LaTeX, Perl, Intel Compiler Suite, CVS, SVN, InstallShield, Cygwin, Virtualization, Java, Linux System Administration, Mercurial, Avionics, LynxOS-178
% Server setup and administration: SAMBA, NFS, Apache, NTP, VNC, SSH
% Virtualization Tools: VMware Server, Sun Microsystems Virtualbox

\hypersetup{
        colorlinks = true,
        urlcolor = black,
        pdfauthor = {\name},
        pdfkeywords = {\name, \skills},
        pdftitle = {\name's Resume},
        pdfsubject = {\name},
        pdfpagemode = UseNone
}

\geometry{
        body={6.5in, 8.5in},
        left=1.0in,
        top=1.0in
}

% Don't indent paragraphs.
\setlength\parindent{0em}


% Customize page headers
\fancypagestyle{first}
{
    \fancyhf{}
    \setlength{\headheight}{1.0in}
    \renewcommand{\headrule}{\vspace{0.125in} \hrule}
    \fancyhead[L]{
        {\huge \name}\\
        \vspace{0.125in}
        \parbox{0.5\textwidth}{
            \address\\
            \city, \state\ \zip
        }
    }
    \fancyhead[R]{
        \parbox{0.5\textwidth}{
            Mobile: \phone \\
            Email: \texttt{\email} \\
            LinkedIn: \texttt{\url{\webpage}}
        }
    }
}

\setlength{\headheight}{15.2pt}
\pagestyle{fancy}
\markright{\name}
\thispagestyle{first}

% formatting for the job descriptions
\newenvironment{job_desc}
    {
        \begin{small}
    }
    {
        \end{small}
    }

\newenvironment{job_title}
	{
		\begin{small}
		\bfseries	
	}
	{
		\end{small}
	}

\begin{document}

\section*{SUMMARY}
		\small
        Experienced Software Engineer specializing in safety-critical embedded software development with a focus on avionics and aerospace applications.
        
\section*{EDUCATION}
		\small
        Bachelor of Science in Computer Science, Portland State University, 2012
        
\section*{EMPLOYMENT HISTORY}
    \begin{minipage}[t]{1\textwidth}

        \subsection*{Blue Origin}
        	\begin{job_title}
            New Glenn Embedded Controllers - Kent, WA \\
            March 2021 - July 2025 \\
            Software Engineer\\
        	\end{job_title}
            \begin{job_desc}
            Wrote drivers and middleware for a custom BLDC motor controller board intended for actuating throttle valves.
            Contributed updates to upstream board support and math libraries in order to improve performance and take
            full advantage of the FPU in the ARM processor on that motor controller. Worked with controls engineers to integrate
            simulink model-generated code for the motor control algorithms and provided software support during controls
            tuning and test operations. Between March 2021 and July 2021 time was split 50/50 between NG and NS programs.
            \end{job_desc}
            \newline
            
			\begin{job_title}
            New Shepard Software Architecture - Kent, WA \\
            May 2019 - July 2021 \\
            Software Integration Engineer\\
            \end{job_title}
            \begin{job_desc}
            Incorporated software updates to different systems on the New Shepard propulsion module, wrote tests for
            verifying that the software complies with system-level requirements, as well as creating and updating tools and supporting
            infrastructure to streamline the testing process. Provided technical advice and schedule estimates to management stakeholders.
            Provided engineering back-room support, troubleshooting software problems and providing guidance to spacecraft flight controllers
            during flight operations.
            \end{job_desc}
            \newline

        \subsection*{Aerotek}
            \begin{job_title}
            Blue Origin, New Shepard Software Architecture - Kent, WA \\
            November 2018 - May 2019 \\
            Software Integration Engineer\\
            \end{job_title}
            \begin{job_desc}
                Working on software integration and testing for the New Shepard spacecraft and associated equipment for Blue Origin, as a contract employee.
            \end{job_desc}
            \newline

        \subsection*{Rockwell Collins}
        	\begin{job_title}
            Head Up Guidance Systems - Wilsonville, OR \\
            March 2013 - August 2018 \\
            Software Engineer\\
            \end{job_title}
            \begin{job_desc}
            Developing embedded avionics software for heads-up displays in compliance with a DO-178 B/C Software Assurance Level A process.
            \end{job_desc}

    \end{minipage}


\section*{SKILLS}
        \skills


\vfill\center{\tiny{Last updated: \today}}

\end{document}
